\documentclass[11pt,a4paper,sans]{moderncv}
\usepackage{url}

% ModernCV themes
\moderncvstyle{banking}
\moderncvcolor{blue}

% Encoding
\usepackage[utf8]{inputenc}
\usepackage[scale=0.85]{geometry}

% Personal data
\name{Alberto}{Damo}
\title{Kernel \& Systems Software Developer}
\address{Padova, Italy}{}
\email{alberto.damo@proton.me}
\homepage{github.com/mrmonopoly-cyber}
\social[linkedin]{alberto-damo-62b81b23a}
\extrainfo{Master’s Student in Computer Science}

\begin{document}
\makecvtitle

%----------------------------------------------------------------------------------------
% PROFILE
%----------------------------------------------------------------------------------------
\section{Profile}
Embedded systems and firmware engineer specialising in low-level C programming, operating system
internals and bare-metal development. Proven track record in automotive-grade MCU environments,
multi-core real-time systems, CAN-bus communication architecture and tooling for calibration \&
diagnostics. Seeking to leverage deep technical expertise in a role focused on high-reliability
systems and Linux/kernel integration.
%----------------------------------------------------------------------------------------
% TECHNICAL SKILLS
%----------------------------------------------------------------------------------------
\section{Technical Skills}
\cvitem{Programming}{C (expert), Rust, C\texttt{++},Assembly (x86\_64 GAS basics), Bash, Golang, Java, Haskell, F\#}
\cvitem{Systems}{Linux internals, bootloaders, UEFI, memory management, kernel architecture}
\cvitem{Embedded}{AURIX TC375 (TriCore), tricore-elf-gcc, linker scripts, GPIO \& CAN control, Arduino}
\cvitem{Tools}{Git, GCC, GDB, QEMU, OVMF (Tianocore), libgpiod, SocketCAN}
\cvitem{Concepts}{Concurrency, interrupts, synchronization, atomic operations, virtualization fundamentals}

%----------------------------------------------------------------------------------------
% EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\cventry{Expected 2026}{Master’s Degree in Computer Science}{University of Padua}{}{}{
  Focus areas: Operating Systems, Embedded Systems, Computer Architecture.}

\cventry{2019--2023}{Bachelor’s Degree in Computer Science}{University of Udine}{}{}{
Graduated with a focus on Software Engineering, Systems Programming, and Distributed Systems.}

%----------------------------------------------------------------------------------------
% EXPERIENCE
%----------------------------------------------------------------------------------------
\section{Experience}

\cventry{2024--2025}{\textbf{ Software Department Member }}{RaceUp Formula SAE Team}{}{}{
\begin{itemize}%
  \item Member of the software department of \textbf{RaceUp}, the official Formula SAE team of the University of Padua.
  \item Designed and implemented the \textbf{ControlUnitLogicOperator} project: the MCU for Raceup team racing car with its own car emulator to test the code.
  \item Developed a \textbf{Safety Critical System (SCS)} with atomic synchronization across threads and real-time exception handling.
  \item Created the \textbf{DPS (Debug Peripheral System)} and \textbf{DPS CLI} to provide live debugging and telemetry of GPIO and CAN signals.
  \item \textbf{Repositories:} \url{https://github.com/mrmonopoly-cyber/ControlUnitLogicOperator}, \url{https://github.com/mrmonopoly-cyber/DPS}, \url{https://github.com/mrmonopoly-cyber/dps_cli}
\end{itemize}}

\cventry{2023}{\textbf{ DevOps Developer}}{ Nucleus S.r.l.}{}{}{
\begin{itemize}%
  \item Contributed to infrastructure automation and software deployment pipelines.
  \item Forked and extended \textbf{Qmerge (Gentoo portage-utils)} to enhance dependency handling and CI behavior.
  \item Worked with system-level Linux tools, package management, and scripting for system provisioning.
  \item \textbf{Repository:} \url{https://github.com/mrmonopoly-cyber/portage-utils}
\end{itemize}}

\cventry{2023}{\textbf{ Cloud Engineer Intern}}{ Nucleus S.r.l. (Udine, Italy)}{}{}{
\begin{itemize}%
  \item Worked on distributed storage and orchestration solutions using \textbf{Ceph} and \textbf{Kubernetes}.
  \item Assisted in configuring and maintaining on-premise and hybrid cloud clusters.
  \item Focused on performance optimization and deployment automation.
\end{itemize}}

%----------------------------------------------------------------------------------------
% PROJECTS
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
% SELECTED PROJECTS
%----------------------------------------------------------------------------------------
\section{Selected Projects}

\cventry{2025--Present}{\textbf{UEFI-Compliant OS}}{Custom Operating System from Scratch}{}{}{
  \begin{itemize}%
    \item \textbf{Role:} Sole Developer
    \item \textbf{Technologies:} Rust, Assembly, QEMU, UEFI (OVMF/Tianocore)
    \item \textbf{Problem/Scope:} Educational project aimed at understanding early boot stages and kernel initialization by implementing a custom UEFI-compliant operating system from raw specifications.
    \item \textbf{Contribution/Impact:} Implemented a Rust-based UEFI disk image generator and bootloader with memory initialization, console I/O, and early process management. Demonstrated full UEFI compliance and successful QEMU execution.
  \end{itemize}}

\cventry{2024--2025}{\textbf{ControlUnitLogicOperator}}{Multi-Core Engine Control Software}{}{}{
  \begin{itemize}%
    \item \textbf{Role:} Lead Developer
    \item \textbf{Technologies:} C (bare-metal), AURIX TC375 (TriCore), SocketCAN, libgpiod, Doxygen
    \item \textbf{Problem/Scope:} Developed a real-time multi-core control unit for the Formula SAE racing car without access to a Hardware-in-the-Loop setup. Designed and implemented a software emulator to test system behavior under real-time conditions.
    \item \textbf{Contribution/Impact:} Built and deployed software managing telemetry, engine control, input handling, safety logic, and torque vectoring across three cores. Designed a thread-safe Safety Critical System with atomic synchronization and a runtime trace stack for diagnostics. Successfully used during Formula SAE races in both human and AI driving modes.
    \item \textbf{Repository:} \url{https://github.com/mrmonopoly-cyber/ControlUnitLogicOperator}
  \end{itemize}}

\cventry{2024--2025}{\textbf{Debug Peripheral System (DPS)}}{Runtime Debugging Interface}{}{}{
  \begin{itemize}%
    \item \textbf{Role:} Lead Developer
    \item \textbf{Technologies:} C, CAN bus (no external libraries)
    \item \textbf{Problem/Scope:} Designed a platform-independent master/slave architecture for real-time debugging and calibration over CAN, capable of managing up to 16 slave boards through a single master node using one message ID.
    \item \textbf{Contribution/Impact:} Implemented a CLI tool for live discovery of tunable parameters, RAM modification, and calibration across multiple boards. Actively used in testing and race tuning to adjust engine power limits and performance parameters.
    \item \textbf{Repository:} \url{https://github.com/mrmonopoly-cyber/DPS}
    \item \textbf{Repository:} \url{https://github.com/mrmonopoly-cyber/dps_cli}
  \end{itemize}}

\cventry{2024}{\textbf{Arithmetic Combinators Interpreter}}{Proof-of-Concept for Expression Evaluation}{}{}{
  \begin{itemize}%
    \item \textbf{Role:} Sole Developer \\
    \item \textbf{Technologies:} Rust (no external libraries)
    \item \textbf{Problem/Scope:} Exam project inspired by personal research into Interaction Combinators as a model of computation.
    \item \textbf{Contribution/Impact:} Designed and implemented a Rust-based interpreter capable of parsing and computing arithmetic expressions with addition, subtraction, multiplication, and division through graph-based reduction.
    \item \textbf{Repository:} \url{https://github.com/mrmonopoly-cyber/arithmetic_combinators}
  \end{itemize}}

\cventry{2024}{\textbf{Raft Project Runtime}}{Distributed Computing Cluster}{}{}{
  \begin{itemize}%
    \item \textbf{Role:} Sole Developer
    \item \textbf{Technologies:} Go, ArchISO, libvirt
    \item \textbf{Problem/Scope:} Research and exam project aimed at building a reproducible, easily deployable distributed VM cluster implementing the RAFT consensus algorithm.
    \item \textbf{Contribution/Impact:} Developed a fully automated cluster orchestration runtime capable of dynamically resizing while maintaining RAFT consistency. Enabled deterministic multi-node boot environments for distributed systems experimentation.
    \item \textbf{Paper link:} \url{https://www.linkedin.com/feed/update/urn:li:activity:7298456277242806272/}
    \item \textbf{Repository:} \url{https://github.com/mrmonopoly-cyber/raft_project_runtime}
  \end{itemize}}

\cventry{2023}{\textbf{Portage-Utils (qmerge fork)}}{Extended Gentoo’s qmerge utility for DevOps automation}{Nucleus S.r.l.}{}{
  \begin{itemize}%
    \item \textbf{Role:} Sole Developer
    \item \textbf{Technologies:} C
    \item \textbf{Problem/Scope:} Forked a customized version of Gentoo’s \texttt{qmerge} utility to add functionality for internal deployment workflows.
    \item \textbf{Contribution/Impact:} Reduce update time of company's servers from 12h to ~2h hours
    \item \textbf{Repository:} \url{https://github.com/mrmonopoly-cyber/portage-utils}
  \end{itemize}}

%----------------------------------------------------------------------------------------
% SOFT SKILLS
%----------------------------------------------------------------------------------------
\section{Soft Skills}
\cvitem{Leadership}{Managed a software team and trained junior engineers in embedded and systems programming.}
\cvitem{Process Improvement}{Identified inefficiencies in workflows and implemented innovative solutions, including the design of the Debug Peripheral System (DPS) to streamline debugging and calibration processes.}
\cvitem{Creativity \& Problem Solving}{Develops novel solutions for complex engineering challenges through creative thinking and practical innovation.}

%----------------------------------------------------------------------------------------
% ADDITIONAL INFO
%----------------------------------------------------------------------------------------
\section{Additional Information}
\cvitem{Languages}{
\textbf{English:} B2 \\
\textbf{Italian:} C2 (Native)\\
}
\cvitem{Interests}{Kernel development, virtualization, firmware development}
\cvitem{Goal}{To expand my expertise in kernel and systems programming by challenging myself with new projects}


\end{document}

